---
title: "dfam_handler"
author: "Quanyuan He"
date: "2018/8/8"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# A introduction of Dfam databases 
Dfam :[link](http://www.dfam.org/)

## Define global setting
```{r}
DFAM_URL= "http://www.dfam.org"
DFAM_VERSION = "2.0"
DFAM_DATABASE_DIR = "/Users/quanyuanhe/OneDrive/MyProjects/repetative_seq/data_source/our_database/Dfam"
```

## Download pfam rnph_hit files and load it to workspace.
```{r}
library(HelpersMG)
library(R.utils)
library(reshape2)
setwd(DFAM_DATABASE_DIR)

# Function to Dfam for nrph.hits
# TSV list of all non-redundant matches found in the
# given assembly and that score above the GA threshold
getDfamNrphHits = function (db_dir, version, genome){
  gz_file_url = paste(genome,"_dfam.nrph.hits.gz",sep="")
  print(gz_file_url)
  file_url = paste(genome,"_dfam.nrph.hits",sep="")
  print(file_url)
  wget_url = paste("http://www.dfam.org/web_download/Release/Dfam_",as.character(version),"/",gz_file_url, sep="")
  gz_file_path = paste(db_dir,gz_file_url,sep='/')
  file_path = paste(db_dir,file_url,sep='/')
  if (!file.exists(gz_file_path) && !file.exists(file_path)){
    hit.gz <- wget(wget_url)
  }
  file_path = paste(db_dir,file_url,sep='/')
  if (!file.exists(file_path)){
    gunzip(gz_file_path)
  }
  result = read.csv(file_url, nrows=-1, header = FALSE, sep = "\t", comment.char="#", quote = "\"'", row.names = NULL)
  colnames(result) = c('seq_name','model_acc','model_name','bit_score','e-value','-','hmm_start','humm_end','hmm_length',
              'strand','align_start','align_end','envolope_start','envolope_end','seq_length','NA','description')
  return (result)
}

hg38_nrph_hits = getDfamNrphHits(DFAM_DATABASE_DIR, DFAM_VERSION, "hg38")
mm10_nrph_hits = getDfamNrphHits(DFAM_DATABASE_DIR,DFAM_VERSION,"mm10")

```
```{r}

# Filter re_hit with full-length model match
hg38_nrph_hits = hg38_nrph_hits[(hg38_nrph_hits$humm_end-hg38_nrph_hits$hmm_start+1)/hg38_nrph_hits$hmm_length>0.85,]


class_infor=hg38_re_tab[,c(11,12,13)]
class_infor = unique.data.frame(class_infor)
m1 <- merge(hg38_nrph_hits, class_infor, by.x = "model_name", by.y = "repName", all.x = TRUE)
#LINE1
indexes = which(grepl(c("LINE2"), m1$description))
levels(m1$repClass)= c(levels(m1$repClass),'LINE')
m1[indexes,]$repClass = "LINE"
levels(m1$repFamily)= c(levels(m1$repFamily),'L1')
m1[indexes,]$repFamily = "L2"

#LINE1
indexes = which(grepl(c("L1"), m1$description))
levels(m1$repClass)= c(levels(m1$repClass),'LINE')
m1[indexes,]$repClass = "LINE"
levels(m1$repFamily)= c(levels(m1$repFamily),'L1')
m1[indexes,]$repFamily = "L1"

indexes = which(grepl(paste(c("satellite","Satellite"),collapse="|"), m1$description))
levels(m1$repClass)= c(levels(m1$repClass),'satellite')
m1[indexes,]$repClass = "satellite"
levels(m1$repFamily)= c(levels(m1$repFamily),'satellite')
m1[indexes,]$repFamily = "satellite"

#DNA transposon


indexes = which(grepl(paste(c('DNA transposon'),collapse="|"), m1$description))
levels(m1$repClass)= c(levels(m1$repClass),'DNA')
m1[indexes,]$repClass = "DNA"
#levels(m1$repFamily)=c(levels(m1[indexes,]),as.character(unique(m1[indexes,]$model_name)))
levels(m1$repFamily)= c(levels(m1$repFamily),'DNA')
m1[indexes,]$repFamily = 'DNA'

indexes = which(grepl(paste(c('Charlie'),collapse="|"), m1$description))
levels(m1$repClass)= c(levels(m1$repClass),'DNA')
m1[indexes,]$repClass = "DNA"
levels(m1$repFamily)= c(levels(m1$repFamily),'Charlie')
m1[indexes,]$repFamily = 'Charlie'

#*_DNA
indexes = which(grepl(paste(c("_DNA"),collapse="|"), m1$model_name))
levels(m1$repClass)= c(levels(m1$repClass),'DNA')
m1[indexes,]$repClass = "DNA"
levels(m1$repFamily)= c(levels(m1$repFamily),'TcMar')
m1[indexes,]$repFamily = "TcMar"

m1[which(is.na(m1$repClass)),]$repClass='Unknown'
levels(m1$repFamily)= c(levels(m1$repFamily),'Unknown')
m1[which(is.na(m1$repFamily)),]$repFamily='Unknown'

hg38_nrph_hits = m1
hg38_nrph_hits$align_len = abs(hg38_nrph_hits$align_end - hg38_nrph_hits$align_start)
m1 = NULL
```

```{r}
hg38_re_full_LINE = hg38_nrph_hits[grepl("L1|L2|CR1", hg38_nrph_hits$repFamily),]
hist(hg38_re_full_LINE$align_len, breaks=20)
hg38_re_full_LINE = hg38_re_full_LINE[hg38_re_full_LINE$align_len>5000,]
hist(hg38_re_full_LINE$align_len, breaks=20)
# Left join with repbase
# This doesn't work because the model difinitions are different between UCSC and 
m1 <- merge(hg38_re_full_LINE, repbase_tab, by.x = "model_id", by.y = "MOD")
```

#ERVL
indexes = which(grepl(paste(c("ERVL"),collapse="|"), m1$description))
levels(m1$repClass)= c(levels(m1$repClass),'LTR')
m1[indexes,]$repClass = "LTR"
levels(m1$repFamily)= c(levels(m1$repFamily),'ERVL')
m1[indexes,]$repFamily = "ERVL"

#ERV1
indexes = which(grepl(paste(c("ERV1"),collapse="|"), m1$description))
levels(m1$repClass)= c(levels(m1$repClass),'LTR')
m1[indexes,]$repClass = "LTR"
levels(m1$repFamily)= c(levels(m1$repFamily),'ERV1')
m1[indexes,]$repFamily = "ERV1"

#ERVK
indexes = which(grepl(paste(c("ERVK"),collapse="|"), m1$description))
levels(m1$repClass)= c(levels(m1$repClass),'LTR')
m1[indexes,]$repClass = "LTR"
levels(m1$repFamily)= c(levels(m1$repFamily),'ERVK')
m1[indexes,]$repFamily = "ERVK"
```



## Extract int sequences of REs
```{python}
import numpy
print('hqyone')
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
